A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-30 reviews/response.Rmd

# Reviewer 1 comments {-}

> More mini examples embeded throughout the manuscript. Mainly it didn't showcase to me tsibble's capability well enough but understandably this may make the manuscript long and may be better left to vignettes.

Thanks for this comment. We have decided to mostly leave these to the vignettes, which are readily available on the web page for the package. The reason for doing this is that we feel that having many mini examples interrupts the flow of the paper. We have made two additions, though, which hopefully address these comments.

A new code snippet (featuring new `pedestrian` dataset) is added to subsection 4.4. This is new part added to the paper, summarising the transformation and modeling parts of the data pipeline section. A new example is added that showcases how tsibble provides a platform to forecasting. We also include an energy consumption case study in Section 6.2, illustrating the cleaner, and more expressive, temporal data modeling pipeline.

@@

> I hold a similar sentiment regarding the calendar plot in Figure 12. It's a great plot but I don't necessary think this is a plot that show cased the benefit of tsibble.

Yes, the calendar plot just requires a data frame. We've added the forecasting example to back up this plot: how the weather information improves the demand forecasts.

> Figure 11 with missing data was a great demonstration for tsibble and the data times series pipeline shown in Figure 3. It may be helpful to reduce the opacity of the points as there is a lot of overplotting. The top line which lumps a number of customers together is not particularly informative here. Perhaps it is better replaced with a histogram.

Thanks. We separated the remaining customers to the bottom panel with points of some transparency. We have kept the line range plot instead of a histogram. Because the range plot is more informative: individual missings are congregated in January and February with sporadic continuous missings over the rest of the year.

### 2019-08-30 cover-letter/cover-letter.Rmd
updated cover letter

Please consider our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data," for publication in the Journal of Computational and Graphical Statistics.

This paper proposes a new data abstraction to represent temporal data, referred to as "tsibble", allowing the "tidy data" principles to be brought to the time domain. It helps to reduce the pain from going raw data to model-ready time series data. The tsibble data structure lays the plumbing for time series data analysis modules of transformation, visualization and modeling, to achieve rapid iteration in gaining data insights. The infrastructure of tidy temporal data and tools has been implemented in the R package `tsibble`, which is on CRAN. The paper is written in RMarkdown, which contains the R code to reproduce the results.

The `tsibble` package won the 2019 John Chambers Statistical Software Award. It also lays the foundation of a new ecosystem for tidy time series analysis, known as "tidyverts", including data sets (the `tsibbledata` package), time series statistical methods (the `feasts` package), and forecasting (the `fable` package).

We believe that this manuscript is a good fit for the Journal of Computational and Graphical Statistics, because it provides tidy methodology to make time series analysis easier. Because the software has already received considerable attention, we expect that the work will be of interest to readers of the journal.

>>>>

We have undertaken major revision on our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data," based on reviewers' comments.

We have rewritten Section 3 "Contextual semantics" and Section 4 "Temporal data pipelines". Now Section 3 gives a definition of tsibble in relation to tidy data. Section 4 describes a big picture about each module with the focus of temporal data instead of time series before.

A detailed response letter to reviewers has been provided.

We believe that this manuscript has been significantly improved, that is a good fit for the Journal of Computational and Graphical Statistics.
